---
title: "Passey model report"
author: "Sarah Pederzani"
output: html_document
params:
  project: Axlor
  tooth: toothname
  date: !r Sys.Date()
  Emeasparams: list
  Edist: vector
  mSolvparams: list
  DPE: vector
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

### Model Information

Project: `r params$project`

Tooth ID: `r params$tooth`

Model run date: `r params$date`

### Emeas

Emeas input parameters:

```{r emeasin}
print(params$Emeasparams)
```

notes:

numtrials - number of trials to run iteration  
numsam - number of isotope samples/values  
r1 - (real) isotope 1 sigma reproducibility  
r2 - (integer) sample length 1 sigma reproducibility (in mm * 10)  
r3 - (integer) sample depth 1-sigma reproducibility (in mm * 10)  
la - (integer) length of apposition (in mm * 10)  

Emeas output:

```{r emeasout}

hist(params$Edist)


```

mean(E~meas~) = `r round(mean(params$Edist),2)`

note: Edist is a vector of estimated measurement error (E~meas~) for each trial

### mSolv

mSolv input parameters:

```{r mSolvin}
print(params$mSolvparams)
```

notes:

nsolxns - number of solutions to be computed  
openindx - degree of openendedness, less than lm, openended (profile mature) --> index = 1; close ended (enamel immature) index = lm  
lm - length of maturation  
la - (integer) length of apposition (in mm * 10)  
finit - volumetric fraction of mineral in immature enamel compared to mature enamel  
maxlength - maximum sampling length  
minlength - minimum sampling length (must be > 2)  
mindepth - minumum sampling depth  
r1 - (real) isotope 1 sigma reproducibility  
r2 - (integer) sample length 1 sigma reproducibility (in mm * 10)  
r3 - (integer) sample depth 1-sigma reproducibility (in mm * 10)  
maxratio - max value of the generated reference vector (choose close to average of actual isotope value)  
minratio - min value of the generated reference vector (choose close to average of actual isotope value)  
stdev - sd for random draws that produce reference vector  
df - damping factor. Needs to be chosen to minimize difference between the estimated measurement error (E~meas~) and the prediction error (E~pred~)

```{r mSolvout}

hist(params$DPE)


```

mean(E~pred~) = `r round(mean(params$DPE),2)`

note: DPE is a vector of prediction error (E~pred~) for each trial. It should be close to E~meas~


